\mytitle

### 2016-10-26 paper.tex
paper.tex - fix affiliation:missing new line

\author{Egon W.~Stemle \\
    Institute for Specialised Communication and Multilingualism \\
    EURAC Research \\
    Bolzano/Bozen, Italy
    {\tt egon.stemle@eurac.edu}}

>>>>

\author{Egon W.~Stemle \\
    Institute for Specialised Communication and Multilingualism \\
    EURAC Research \\
    Bolzano/Bozen, Italy \\
    {\tt egon.stemle@eurac.edu}}
